---
title: "Carbapenemase Project"
format: html
author: "Yi-Ju Tseng"
editor: visual
---

# FirstAll vs. Conventional

```{r, message=FALSE, warning=FALSE}
#| echo: false
library(readxl)
library(tidyverse)
library(cvms)
library(patchwork)
```

```{r, message=FALSE, warning=FALSE}
#| echo: false
df.bd = read_excel("20221115_CPO_BD_KP.xlsx",sheet = "Raw")[,1:10]
df.w = read_excel("20221116_CPO_WANG_KP.xlsx",sheet = "KP")
```

```{r}
#| echo: false
########################################
#pre-processing
########################################
df.bd$ID = df.bd$ID %>% 
  str_sub(start = 5,end = 12)

df.bd = df.bd %>% 
  filter(BAC %in% c("Klebsiella pneumoniae"))

df.w$ID=df.w$ID %>% as.character()
```

```{r}
#| echo: false
########################################
#merge
########################################
df.merge = left_join(df.bd,df.w,by = "ID")
df.merge$mCIM.y = df.merge$mCIM.y %>% 
  str_replace(pattern = "\\+", 
              replacement = "1") %>% 
  str_replace( pattern = "\\-", 
              replacement = "0")
df.merge$eCIM.y = df.merge$eCIM.y %>% 
  str_replace(pattern = "\\+", 
              replacement = "1") %>% 
  str_replace( pattern = "\\-", 
              replacement = "0")
```

```{r}
#| echo: false
########################################
#stats
########################################
#df.merge<-df.merge %>% rename(Conventional=mCIM.x,FirstAll=mCIM.y)
#mat=cbind(df.merge$mCIM.x,df.merge$mCIM.y) %>% as.data.frame()
#colnames(mat) = c("Conventional","FirstAll")
df.merge=df.merge %>% 
  filter(mCIM.x %in% c(0,1)) %>% 
  filter(mCIM.y %in% c(0,1))
df.merge$mCIM.x<-ifelse(df.merge$mCIM.x==0,"(-)","(+)")
df.merge$mCIM.y<-ifelse(df.merge$mCIM.y==0,"(-)","(+)")
df.merge$eCIM.x<-ifelse(df.merge$eCIM.x==0,"(-)","(+)")
df.merge$eCIM.y<-ifelse(df.merge$eCIM.y==0,"(-)","(+)")
mCIM.comp=table(df.merge$mCIM.x,df.merge$mCIM.y) 
dimnames(mCIM.comp)[[1]]<-c("Conventional-mCIM(-)","Conventional-mCIM(+)")
dimnames(mCIM.comp)[[2]]<-c("FirstAll-mCIM(-)","FirstAll-mCIM(+)")
mCIM.comp
# write.csv(mCIM.comp,"mCIM.comp_KP.csv",row.names = TRUE)
```

```{r warning=FALSE,fig.height=4,fig.width=4}
#| echo: false

eval <- evaluate(
  data = df.merge,
  target_col = "mCIM.x",
  prediction_cols = "mCIM.y",
  type="binomial",
  positive = "(+)"
)
plot_confusion_matrix(eval,
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="Conventional",y="FirstAll")
ggsave("Con_vs_FirstAll.pdf",device = "pdf",width = 4,height = 4)
```

# MPCR vs. CARBA5

```{r warning=FALSE, message=FALSE}
#| echo: false
#MixTable <- read_excel("CONFUSION MATRIX TABLE.xlsx", 
#    sheet = "Mix")
#MixTable$ID<-as.character(MixTable$ID)
source("Carbapenemase.R")
FinalCM<-FinalCM%>%filter(!is.na(MPCR))

FinalCM %>%
  group_by(SPECIES,GENE) %>%
  summarise(NumberOfPatients=n()) %>%knitr::kable()
```

## Klebsiella pneumoniae

```{r warning=F,message=F}
#| echo: false
KP<-FinalCM %>% filter(SPECIES=="KP") #1500
#eval <- evaluate(
#  data = KP %>% filter(!is.na(MPCR))%>%group_by(GENE),
#  target_col = "MPCR",
#  prediction_cols = "CARBA5",
#  type="binomial",parallel = T
#)
KPGroup<-
  KP %>%
  group_by(GENE,MPCR,CARBA5, .drop = FALSE) %>%
  summarise(N=n()) %>% 
  rename(Prediction=CARBA5,Target=MPCR)%>%
  ungroup() %>%
  complete(Prediction, Target, GENE, fill = list(N = 0)) 


(plot_confusion_matrix(KPGroup %>% filter(GENE=="IMP"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="IMP"))+
(plot_confusion_matrix(KPGroup %>% filter(GENE=="KPC"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="KPC"))+
(plot_confusion_matrix(KPGroup %>% filter(GENE=="NDM"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="NDM"))+
(plot_confusion_matrix(KPGroup %>% filter(GENE=="OXA"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="OXA"))+
(plot_confusion_matrix(KPGroup %>% filter(GENE=="VIM"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="VIM"))
```

## Escherichia coli

```{r warning=F,message=F}
#| echo: false
EC<-FinalCM %>% filter(SPECIES=="EC") #1500
eval <- evaluate(
  data = EC %>% filter(GENE!="IMP")%>%group_by(GENE),
  target_col = "MPCR",
  prediction_cols = "CARBA5",
  type="binomial",parallel = T
)
ECGroup<-
  EC %>%
  group_by(GENE,MPCR,CARBA5, .drop = FALSE) %>%
  summarise(N=n()) %>% 
  rename(Prediction=CARBA5,Target=MPCR)%>%
  ungroup() %>%
  complete(Prediction, Target, GENE, fill = list(N = 0)) 
(plot_confusion_matrix(ECGroup %>% filter(GENE=="IMP"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="IMP"))+
(plot_confusion_matrix(ECGroup %>% filter(GENE=="KPC"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="KPC"))+
(plot_confusion_matrix(ECGroup %>% filter(GENE=="NDM"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="NDM"))+
(plot_confusion_matrix(ECGroup %>% filter(GENE=="OXA"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="OXA"))+
(plot_confusion_matrix(ECGroup %>% filter(GENE=="VIM"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="VIM"))
```

## Enterobacter cloacae complex

```{r warning=F,message=F}
#| echo: false
ECC<-FinalCM %>% filter(SPECIES=="ENT.CLOACAE") #1500
eval <- evaluate(
  data = ECC %>% filter(GENE!="VIM")%>%group_by(GENE),
  target_col = "MPCR",
  prediction_cols = "CARBA5",
  type="binomial",parallel = T
)
ECCGroup<-
  ECC %>%
  group_by(GENE,MPCR,CARBA5, .drop = FALSE) %>%
  summarise(N=n()) %>% 
  rename(Prediction=CARBA5,Target=MPCR)%>%
  ungroup() %>%
  complete(Prediction, Target, GENE, fill = list(N = 0)) 
(plot_confusion_matrix(ECCGroup %>% filter(GENE=="IMP"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="IMP"))+
(plot_confusion_matrix(ECCGroup %>% filter(GENE=="KPC"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="KPC"))+
(plot_confusion_matrix(ECCGroup %>% filter(GENE=="NDM"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="NDM"))+
(plot_confusion_matrix(ECCGroup %>% filter(GENE=="OXA"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="OXA"))+
(plot_confusion_matrix(ECCGroup %>% filter(GENE=="VIM"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="VIM"))
```

## CITRO.FREUNDII

```{r warning=F,message=F}
#| echo: false
CF<-FinalCM %>% filter(SPECIES=="CITRO.FREUNDII") #1500
eval <- evaluate(
  data = CF %>%group_by(GENE),
  target_col = "MPCR",
  prediction_cols = "CARBA5",
  type="binomial",parallel = T
)
CFGroup<-
  CF %>%
  group_by(GENE,MPCR,CARBA5, .drop = FALSE) %>%
  summarise(N=n()) %>% 
  rename(Prediction=CARBA5,Target=MPCR)%>%
  ungroup() %>%
  complete(Prediction, Target, GENE, fill = list(N = 0)) 
(plot_confusion_matrix(CFGroup %>% filter(GENE=="IMP"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="IMP"))+
(plot_confusion_matrix(CFGroup %>% filter(GENE=="KPC"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="KPC"))+
(plot_confusion_matrix(CFGroup %>% filter(GENE=="NDM"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="NDM"))+
(plot_confusion_matrix(CFGroup %>% filter(GENE=="OXA"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="OXA"))+
(plot_confusion_matrix(CFGroup %>% filter(GENE=="VIM"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="VIM"))
```

## CITRO.KOSERI

```{r warning=F,message=F}
#| echo: false
CK<-FinalCM %>% filter(SPECIES=="CITRO.KOSERI") #1500
eval <- evaluate(
  data = CK %>% filter(!GENE %in% c("NDM","VIM","OXA")) %>%group_by(GENE),
  target_col = "MPCR",
  prediction_cols = "CARBA5",
  type="binomial",parallel = T
)
CKGroup<-
  CK %>%
  group_by(GENE,MPCR,CARBA5, .drop = FALSE) %>%
  summarise(N=n()) %>% 
  rename(Prediction=CARBA5,Target=MPCR)%>%
  ungroup() %>%
  complete(Prediction, Target, GENE, fill = list(N = 0)) 
(plot_confusion_matrix(CKGroup %>% filter(GENE=="IMP"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="IMP"))+
(plot_confusion_matrix(CKGroup %>% filter(GENE=="KPC"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="KPC"))+
(plot_confusion_matrix(CKGroup %>% filter(GENE=="NDM"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="NDM"))+
(plot_confusion_matrix(CKGroup %>% filter(GENE=="OXA"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="OXA"))+
(plot_confusion_matrix(CKGroup %>% filter(GENE=="VIM"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="VIM"))
```

## K.AEROGENES

```{r warning=F,message=F}
#| echo: false
KA<-FinalCM %>% filter(SPECIES=="K.AEROGENES") #1500
eval <- evaluate(
  data = KA %>% filter(GENE %in% c("IMP","OXA"))%>%group_by(GENE),
  target_col = "MPCR",
  prediction_cols = "CARBA5",
  type="binomial",parallel = T
)
KAGroup<-
  KA %>%
  group_by(GENE,MPCR,CARBA5, .drop = FALSE) %>%
  summarise(N=n()) %>% 
  rename(Prediction=CARBA5,Target=MPCR)%>%
  ungroup() %>%
  complete(Prediction, Target, GENE, fill = list(N = 0)) 
(plot_confusion_matrix(KAGroup %>% filter(GENE=="IMP"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="IMP"))+
(plot_confusion_matrix(KAGroup %>% filter(GENE=="KPC"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="KPC"))+
(plot_confusion_matrix(KAGroup %>% filter(GENE=="NDM"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="NDM"))+
(plot_confusion_matrix(KAGroup %>% filter(GENE=="OXA"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="OXA"))+
(plot_confusion_matrix(KAGroup %>% filter(GENE=="VIM"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="VIM"))
```

## K.AEROGENES

```{r warning=F,message=F}
#| echo: false
KO<-FinalCM %>% filter(SPECIES=="K.OXYTOCA") #1500
eval <- evaluate(
  data = KO %>% filter(GENE!="IMP")%>%group_by(GENE),
  target_col = "MPCR",
  prediction_cols = "CARBA5",
  type="binomial",parallel = T
)
KOGroup<-
  KO %>%
  group_by(GENE,MPCR,CARBA5, .drop = FALSE) %>%
  summarise(N=n()) %>% 
  rename(Prediction=CARBA5,Target=MPCR)%>%
  ungroup() %>%
  complete(Prediction, Target, GENE, fill = list(N = 0)) 
(plot_confusion_matrix(KOGroup %>% filter(GENE=="IMP"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="IMP"))+
(plot_confusion_matrix(KOGroup %>% filter(GENE=="KPC"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="KPC"))+
(plot_confusion_matrix(KOGroup %>% filter(GENE=="NDM"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="NDM"))+
(plot_confusion_matrix(KOGroup %>% filter(GENE=="OXA"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="OXA"))+
(plot_confusion_matrix(KOGroup %>% filter(GENE=="VIM"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="MPCR",y="CARBA5",title="VIM"))
```

```{r warning=FALSE, message=FALSE}
#| echo: false
#FinalCM %>% filter(SPECIES=="KP") %>%
#  ggplot(aes(x=MPCR))+
#  geom_bar()+
#  facet_grid(paste0("CARBA 5:",CARBA5)~GENE,scales ="free")+
#  scale_x_continuous(breaks = c(0,1))+
#  theme_bw()
```

```{r warning=FALSE, message=FALSE}
#| echo: false
AST<-read_csv("20230307_CPO_BD_AST.csv")
AST<-AST %>% 
  mutate(ID=gsub("CPO-","",B), 
         Marker=ifelse(grepl("Class A|Class D",Marker),
                       "Class A or D Carbapenemase Producer",Marker))
AST$SPECIES<-ifelse(AST$Name=="Klebsiella pneumoniae","KP",
                    ifelse(AST$Name=="Klebsiella oxytoca","K.OXYTOCA",
                           ifelse(AST$Name=="Klebsiella aerogenes","K.AEROGENES",
                                  ifelse(AST$Name=="Escherichia coli","EC",
                                         ifelse(AST$Name=="Enterobacter cloacae complex","ENT.CLOACAE",
                                                ifelse(AST$Name=="Citrobacter koseri","CITRO.KOSERI",
                                                       ifelse(AST$Name=="Citrobacter freundii complex","CITRO.FREUNDII",
                                                              AST$Name)))))))

AST_MPCR<-inner_join(AST,FinalCM,by=c("ID","SPECIES"))
AST_MPCRGroup<-
  AST_MPCR %>% group_by(MPCR,CARBA5,Ab,Res) %>%
  summarise(Count=n())
```


# CPO, mCIM, and eCIM (FirstAll)
```{r warning=FALSE, message=FALSE}
#| echo: false
CPO<-
  AST%>%select(ID,Name,Marker) %>% unique() %>% 
  filter(!is.na(Marker)) 

CIM_KP <- read_excel("20230307_CPO_BD_final.xlsx", 
    sheet = "KP")
CIM_Other <- read_excel("20230307_CPO_BD_final.xlsx", 
    sheet = "other")
col<-c("Accession","Organism","mCIM","eCIM","mCIM/eCIM Result")
CIMAll<-rbind(CIM_KP[,col],CIM_Other[,col])
CIMAll$ID<-gsub("CPO-","",CIMAll$Accession)
table(CIMAll$eCIM)
table(CIMAll$mCIM)
## clean needed
CIMAll$mCIM<-ifelse(CIMAll$mCIM==0,"(-)","(+)")
CIMAll$eCIM<-ifelse(CIMAll$eCIM==0,"(-)","(+)")
CIMAll<-CIMAll %>% filter(!is.na(mCIM)&!is.na(eCIM))
CPO_CIM<-inner_join(CPO,CIMAll,by=c("ID","Name"="Organism"))
```

- mCIM-eCIM- => no carbapenemase detected **(unknown? or NA?)**
- mCIM+eCIM- => class A or D **(How about unknown?)**
- mCIM-eCIM+ => lab error? should be rechecked
- mCIM+eCIM+ => classB **(How about unknown?)**

```{r warning=FALSE, message=FALSE}
#| echo: false
CPO_CIMGroup<-
  CPO_CIM %>% group_by(Name,Marker,mCIM,eCIM) %>%
  summarise(Count=n())%>%
  ungroup() %>%
  complete(Name,Marker, mCIM, eCIM, fill = list(Count = 0)) 

CPO_CIMGroup$Tag<-""
CPO_CIMGroup$Tag<-
  ifelse(CPO_CIMGroup$Marker!="Class A or D Carbapenemase Producer" & CPO_CIMGroup$mCIM=="(+)" & CPO_CIMGroup$eCIM=="(-)",
       "Conflict",CPO_CIMGroup$Tag)
CPO_CIMGroup$Tag<-
  ifelse(CPO_CIMGroup$Marker!="Class B Carbapenemase Producer" & CPO_CIMGroup$mCIM=="(+)"&CPO_CIMGroup$eCIM=="(+)",
       "Conflict",CPO_CIMGroup$Tag)
CPO_CIMGroup$Tag<-
  ifelse(CPO_CIMGroup$Marker!="Carbapenemase Producer" & CPO_CIMGroup$mCIM=="(-)"&CPO_CIMGroup$eCIM=="(-)",
       "Conflict",CPO_CIMGroup$Tag)
CPO_CIMGroup$Tag<-
  ifelse(CPO_CIMGroup$mCIM=="(-)"&CPO_CIMGroup$eCIM=="(+)",
       "Error?",CPO_CIMGroup$Tag)
CPO_CIMGroup$Marker<-gsub(" Producer","",CPO_CIMGroup$Marker)
knitr::kable(CPO_CIMGroup)
```

## Method1: 用Carbapenemase區分，畫三個confusion matrix

### KP
```{r warning=FALSE, message=FALSE}
#| echo: false
CPO_CIMGroup$Target<-CPO_CIMGroup$mCIM
CPO_CIMGroup$Prediction<-CPO_CIMGroup$eCIM
CPO_CIMGroup$N<-CPO_CIMGroup$Count
(plot_confusion_matrix(CPO_CIMGroup %>% 
                         filter(Name=="Klebsiella pneumoniae"&
                                  Marker=="Carbapenemase"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="mCIM",y="eCIM",title="Carbapenemase"))+
(plot_confusion_matrix(CPO_CIMGroup %>% filter(Name=="Klebsiella pneumoniae"&Marker=="Class B Carbapenemase"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="mCIM",y="eCIM",title="Class B Carbapenemase"))+
(plot_confusion_matrix(CPO_CIMGroup %>% filter(Name=="Klebsiella pneumoniae"&Marker=="Class A or D Carbapenemase"),
  counts_on_top=TRUE,add_normalized=FALSE)+
  labs(x="mCIM",y="eCIM",title="Class A or D Carbapenemase"))

```
### Other Bact (TBD)

## Method2: 用bar chart取代三個confusion matrix
```{r warning=FALSE, message=FALSE}
#| echo: false
ggplot(CPO_CIMGroup%>% 
         filter(Name=="Klebsiella pneumoniae"),
       aes(x=mCIM,y=Count,fill=Tag))+
  geom_bar(stat="identity",show.legend = FALSE)+
  facet_grid(paste0("eCIM ",eCIM)~Marker)+
  labs(x="mCIM")+
  theme_bw()+
  scale_fill_manual(values=c("Conflict"="coral1","Error?"="coral4"))
```

### Other Bact (TBD)

## CPO vs. AST

### Not class B, but Ceftazidime-Avibactam R？

- Not class B, but Ceftazidime-Avibactam R
- Ertapenem, Imipenem, Meropenem **每個抗生素分開呈現？**: 
    - MIC vs mCIM/eCIM (TBD)
    - MIC vs MPCR (TBD)
    - MIC vs CARBA5 (TBD)
    - MIC vs CPO (TBD)
    
- 要分菌株嗎？

```{r warning=FALSE, message=FALSE}
#| echo: false
ASTCPO<-AST%>%select(B,Name,Marker,Ab,Res) %>% unique() %>% 
  filter(grepl("^CPO",B)&!is.na(Marker)) %>% 
  mutate(ID=gsub("CPO-","",B), 
         Marker=gsub(" Producer","",Marker),
         MarkerNew=ifelse(Marker=="Carbapenemase","Class Unknown",Marker),
         Res=ifelse(Res=="S","S","R or I"))
ASTCPOGroup<-
  ASTCPO %>% filter(Ab %in% c("Ceftazidime-Avibactam")) %>%
  group_by(Name,Marker,MarkerNew,Ab,Res) %>%
  summarise(Count=n())
knitr::kable(ASTCPOGroup)
```

```{r warning=FALSE, message=FALSE}
#| echo: false
ASTCPOGroup %>% filter(Ab=="Ceftazidime-Avibactam") %>%
  ggplot(aes(x=Res,y=Count,label=Count,fill=Name))+
  geom_bar(stat="identity")+
  #geom_text()+
  scale_fill_brewer(palette = "Dark2")+
  facet_grid(.~Marker)+
  theme_bw()
```

- 換個名字？
```{r warning=FALSE, message=FALSE}
#| echo: false
ASTCPOGroup %>% filter(Ab=="Ceftazidime-Avibactam") %>%
  ggplot(aes(x=Res,y=Count,label=Count,fill=Name))+
  geom_bar(stat="identity")+
  #geom_text()+
  scale_fill_brewer(palette = "Set1")+
  facet_grid(.~MarkerNew)+
  theme_bw()
```